How to Name a Real-World Object, and how not

### 2019-12-06 papers/ACL2020/acl2020_main.tex
[ACL2020] adds tex for related work

\section{Related Work}
\label{sec:related}
%\input{related}

[Sectioning to be revised]

\paragraph{(Entry-Level) Object Names}
Cognitive Science/psycholinguistics:\\
- levels of specificity\\
- basic-level vs. entry-level\\
- object naming studies
Language + Vision:\\
Ordonez et al., Zarriess \& Schlangen, ... \\
- Our work: empirical notion of entry-level

\paragraph{Visual Object Recognition in Computer Vision}
- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image)\\
- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?

>>>>

\section{Related Work}
\label{sec:related}
\input{related}
